---
title: "Train a text classification model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Example of ruimtehol

Wonderful [ruimtehol](https://github.com/bnosac/ruimtehol) package build on top of Facebook research [Starspace](https://github.com/facebookresearch/StarSpace). R packge was there before python ;)

Warning, this might take time, suggesting using VM. Here's example straight out from the package. 
```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(ruimtehol)
data("dekamer", package = "ruimtehol")
dekamer$x <- strsplit(dekamer$question, "\\W")
dekamer$x <- sapply(dekamer$x, FUN = function(x) paste(setdiff(x, ""), collapse = " "))
dekamer$x <- tolower(dekamer$x)
dekamer$y <- strsplit(dekamer$question_theme, split = ",")
dekamer$y <- lapply(dekamer$y, FUN=function(x) gsub(" ", "-", x))

set.seed(123456789)
model <- embed_tagspace(x = dekamer$x, y = dekamer$y,
                        dim = 50, 
                        lr = 0.01, epoch = 40, loss = "softmax", adagrad = TRUE, 
                        similarity = "cosine", negSearchLimit = 50,
                        ngrams = 2, minCount = 2)
plot(model)                        


starspace_save_model(model)
```
Try trained model
```{r message=FALSE, warning=FALSE}
            
text <- c("de nmbs heeft het treinaanbod uitgebreid via onteigening ...",
          "de migranten komen naar europa de asielcentra ...")                   
predict(model, text, k = 3)  
predict(model, "koning filip", k = 10, type = "knn")
predict(model, "koning filip", k = 10, type = "embedding")
```


# Some other data
Data for text classification tasks are out there but not about very interesting topics. Stanford Uni has collected some [Amazon reviews](http://snap.stanford.edu/data/amazon/productGraph/categoryFiles/). 
```{r eval=FALSE, include=FALSE}
library(jsonlite)
library(dplyr)
out <- lapply(readLines("reviews_Pop.json"), fromJSON)

library(data.table)
outdf <- rbindlist(out, use.names=T,fill=TRUE) %>% unique()

outdf %>% 
  group_by(overall) %>% 
  summarise(n=n())

```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#Let's add categories
outdfsample <- outdf %>% 
  mutate(pos_neg = if_else(overall>3, 'GOOD', 'BAD')) %>% 
  sample_frac(0.1)

## Split data
## 75% of the sample size
smp_size <- floor(0.75 * nrow(outdfsample))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(outdfsample)), size = smp_size)

train <- outdfsample[train_ind, ]
test <- outdfsample[-train_ind, ]

```


For the multiclassification problem I selected a Kaggle competition [data](https://www.kaggle.com/jhoward/nb-svm-strong-linear-baseline/data), from Comment Classification Challenge. 
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
train <- read_csv("train.csv")

train %>% head()

```
Let's modify a bit for the StarSpace/ruimtehol required format
```{r}
#collapse labels to one column and select only the ones that have at least one label
library(tidyr)
train_mod <- train %>%
  gather(Variable, Value, -id, -comment_text, na.rm = TRUE) %>%
  filter(!Value %in% 0) %>%
  group_by(id,comment_text) %>%
  summarise(labels = toString(Variable))

  #StarSpace format
  train_mod$x <- strsplit(train_mod$comment_text, "\\W")
  train_mod$x <- sapply(train_mod$x, FUN = function(x) paste(setdiff(x, ""), collapse = " "))
  train_mod$x <- tolower(train_mod$x)
  train_mod$y <- strsplit(train_mod$labels, split = ",")
  train_mod$y <- lapply(train_mod$y, FUN=function(x) gsub(" ", "", x))

#train_mod %>% select(x,y) %>% head(10)
```

## Training the models
Let's train our own
```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
library(ruimtehol)

## TRAIN MODEL for reviews
set.seed(1234)
system.time({
  
  model_toxic <- embed_tagspace(x = train_mod$x, y = train_mod$y,
                          early_stopping = 0.8, validationPatience = 10,
                          dim = 50,
                          lr = 0.01, epoch = 40, loss = "softmax", adagrad = TRUE,
                          similarity = "cosine", negSearchLimit = 50,
                          ngrams = 2, minCount = 2)
})

plot(model_toxic)

starspace_save_model(model_toxic, file = "toxic_textspace.ruimtehol")
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(ruimtehol)

## TRAIN MODEL for reviews
set.seed(1234)
system.time({
  
  model_en <- embed_tagspace(x = train$reviewText, y = train$pos_neg,
                          early_stopping = 0.8, validationPatience = 10,
                          dim = 50,
                          lr = 0.01, epoch = 40, loss = "softmax", adagrad = TRUE,
                          similarity = "cosine", negSearchLimit = 50,
                          ngrams = 2, minCount = 2)
})

plot(model_en)

starspace_save_model(model_en, file = "en_textspace.ruimtehol")
```


### Write functions
```{r}

make_prediction_toxic<- function(x) {
  prediction <- predict(model_toxic, x, k = 5) #type = "labels"
  return(prediction)}

make_prediction_toxic2<- function(x) {
  prediction <- predict(model_toxic, x, type = "labels") #
  return(prediction)}


# make_prediction_en <- function(x) {
#   prediction <- predict(model_en, x, type = "labels")
#   return(prediction)}


```

### Test functions
```{r eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
sometetx <- "FUCK YOUR FILTHY MOTHER IN THE ASS, DRY!"

make_prediction_toxic(sometetx)

make_prediction_toxic2(sometetx)

```
